Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-09-30 doc/paper.Rmd
type 2 error rate figure

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE
)
options(knitr.table.format = "latex")
```

## Introduction

@@

## Toolmarks

@@

```
## Bullets

@@

## Including Plots

For a significance level of 0.05

![](../doc/plots/error_pt05.png)
For a significance level of 0.01

![](../doc/plots/error_pt01.png)

For a significance level of 0.001

![](../doc/plots/error_pt001.png)

![](../doc/plots/rate_pt001.png)

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE
)
options(knitr.table.format = "latex")
library(tidyverse)
```

```{r functions}
errorrate <- function(data, alpha) {
  summ <- data %>% filter(!is.na(p_value)) %>%
    mutate(signif = p_value < alpha) %>%
    group_by(wv, wo, match, signif) %>% tally()
  summ$error <- with(summ, match != signif)
  summ$alpha <- alpha

  rates <- summ %>% group_by(wv, wo, match, alpha) %>% summarize(
    rate = n[error==TRUE]/sum(n)
  )
  rates %>% spread(match,rate) %>% rename(
    actual = `FALSE`,
    beta = `TRUE`
  )
}
```

```{r data}
if (!file.exists("../data/all-sigs.rds")) {
  files <- dir("../data/signatures", pattern="csv")
  all <- data.frame()
  for (file in files) {
    tmp <- read.csv(file=file.path(path="../data/signatures", file)) 
    if (length(grep("x",names(tmp)) > 0)) tmp <- tmp %>% select(-x)
    all <- rbind(all, tmp)
  }
  saveRDS(all, file="../data/all-sigs.rds")
} else {
  all <- readRDS("../data/all-sigs.rds")
}

errors <- rbind(errorrate(all, 0.001), 
                errorrate(all, 0.005), 
                errorrate(all, 0.01), 
                errorrate(all, 0.05))
```

# Introduction

@@

# Toolmarks

@@

```
# Bullets

@@

# Results

## Signatures

Signatures of lands for all Hamby-44 and Hamby-252 scans made available through the NIST ballistics database \citep{nist} were considered.

Figure \ref{fig:type2} gives an overview of type II error rates observed when varying the window size in the optimization step.

```{r type2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $wo$. For a window size of $wo = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $wv$ are typically associated with a smaller type II error."}
greens <- RColorBrewer::brewer.pal(name="Greens", n = 6)
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv))) +
#  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="loess") +
  theme_bw() +
  scale_colour_manual("Nominal type I error", values=greens[-(1:2)]) +
  scale_shape_discrete("Size of \nvalidation window") +
  xlab("Window size for optimization") +
  ylab("Type II error rate")
```
